Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-08 CVPR16/Source/applications.tex
Camera ready version

\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
\begin{table}[!!t]
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\RotText{Initialization by~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ \\
\hline
\end{tabular}
\vspace{-0.25cm}
\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
\label{tab:notations}
\vspace{-0.5cm}
\end{table}

@@

Given 2D image points $\{\bu_j\}$ which are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$. Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$, although called association probability, does not capture the entire information that we have available for computing the association of point tracks to objects.

@@

Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$ as follows
\begin{align}
  P^{ij}_{\text{assoc}} = \frac{1}{Z"}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
  \label{eq:prob-assoc}
\end{align}
where $Z"$ is the new normalization coefficient.

@@

We exploit in this section the application of our continuous occlusion model to 3D object localization in road scenes, which further demonstrates the versatility of the proposed model. Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants, in particular, for each traffic participant, estimating its position $\bp^i(t)$, orientation $\bomega^i(t)$, and 3D dimensions $\bB^i(t)$ on the ground plane. Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.

We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
%
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -\tilde{Z} 
  + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
  + \\ 
  \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
  \left(
    \lambda_{\text{detect}}\EnergyBBox
    + \lambda_{\text{dyn}}\EnergyDyn    
    + \lambda_{\text{size}}\EnergySize
  \right)
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes, while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $\tilde{Z}$ is the normalization coefficient. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. Next, we present our unified continuous occlusion modeling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary material.

@@

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
\end{multline}
where $N$ and $M$ are respectively the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\vspace{-0.3cm}
\paragraph{Inference on graphical model}
We apply Metropolis Hastings method~\cite{mackay1998introduction} for performing inference on the graphical model. Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function. We choose this over alternatives such as block-coordinate descent since they are slower in our experiments.

>>>>

\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
\begin{table}[!!t]
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ \\
\hline
\end{tabular}
\vspace{-0.25cm}
\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
\label{tab:notations}
\vspace{-0.5cm}
\end{table}

@@

Given 2D image points $\{\bu_j\}$ that are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$. Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$, although called association probability, does not capture the entire information that we have available for computing the association of point tracks to objects.

@@

Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$, as follows:
\begin{align}
  P^{ij}_{\text{assoc}} = \frac{1}{Z''}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
  \label{eq:prob-assoc}
\end{align}
where $Z''$ is the new normalization coefficient.

@@

In this section, we exploit our continuous occlusion model for another application, namely, 3D object localization in road scenes, which further demonstrates its versatility. Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants. In particular, for each traffic participant, we wish to estimate its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.

We construct a graphical model for representing relationships among objects, as well as between objects and point tracks. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. The negative log likelihood is decomposed as follows:
%
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -\tilde{Z} 
  + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
  + \\ 
  \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
  \left(
    \lambda_{\text{detect}}\EnergyBBox
    + \lambda_{\text{dyn}}\EnergyDyn    
    + \lambda_{\text{size}}\EnergySize
  \right)
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes, while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $\tilde{Z}$ is the normalization coefficient. Next, we present our unified continuous occlusion modeling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary material.

@@

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
\end{multline}
where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

\vspace{-0.3cm}
\paragraph{Inference on graphical model}
We apply the Metropolis-Hastings method~\cite{mackay1998introduction} to perform inference on the graphical model. Since we optimize over continuous variables, we use the Gaussian distribution as the proposal function. We choose this over alternatives such as block-coordinate descent since they are slower in our experiments.
